Continuation Passing Style for Effect Handlers

### 2020-01-07 docs/article.tex
s/solution/article/g

    As can be seen in the J. Yallop repository \cite{effects-bibliography},
    algebraic effects and handlers are now trending branch of computer science.

@@

    \begin{verbatim}
    handle
        if x == 0 then do ZeroDivisionError ()
                  else return 1/x
    with {
        ZeroDivisionError p r -> return 42 |
        return x -> return x
    }
    \end{verbatim}
    Where we imagine that x variable has been bound previously.

>>>>

    As can be seen in the J. Yallop repository \cite{effects-bibliography},
    algebraic effects and handlers are now trending branch in the computer science.

@@

    \begin{verbatim}
    handle
        if x == 0 then do ZeroDivisionError ()
                  else return 1/x
    with {
        ZeroDivisionError p r -> return 42 |
        return x -> return x
    }
    \end{verbatim}
    Where we imagine that $x$ variable has been bound previously.

    \subsection{Side effects}

    The complexity of the programs and their performance usually comes from side (d)effects.
    Algebraic effects allow us to define code in a declarative manner, and hence
    neatly tame the side effects that they produce. This gives us a lot of flexibility
    in the actual meaning without duplicating the code. Let's consider the following
    very basic code snippet:

    \begin{verbatim}
    let x <- do Fetch () in
    -- operate on x
    \end{verbatim}

    The code is dependent on a context in which it is executed, which here is
    the handler that defines the behaviour of the algebraic \verb!Fetch! effect.
    In the imperative, or even functional approach, we would need to provide
    the interface for fetching the data by doing dependency injection or even
    embedding the operation directly. Here we are just stating what operation
    we are performing, leaving the interpretation up to the execution context,
    which could do the fetching or mock the external resource. \\

    These implications are straightforward when looking from a categorical
    standpoint and models of algebraic theories, nevertheless are very exciting
    for programming use cases. The current Freak implementation does not yet support I/O.
